Interlocks Mitigate Information Cascades in Large-Scale Social Learning

### 2024-10-25 manuscript.tex
Updates Background section.

@@

The above examples all share the same social network structure of small groups connected through mutual membership: {\em interlocks}.
Interlocks have been well-studied in several other contexts.
Perhaps the most well-known is the study of intelocking directorates,
the practice of one individual sitting on the board of directors for
multiple corporations,
allowing an implicit flow of information and influence
\cite{sapinski_interlocking_2018}.
Interlocks arise in other fields as well,
including \cite{fishcer_paul_1994}.

\subsection{Collaboration, Deliberation, etc.}

\subsection{Social Learning}
social influence vs coercion

>>>>

US anti-war protests \cite{detar_intertwinkles:_2013}:
\begin{quote}
The core of these protests were
organized by clusters of small-scale affinity groups. Each affinity
group, consisting of 10 to 20 people, decided what sort of role they
were comfortable fulfilling, and then coordinated with other affinity
groups to participate in larger actions.
\end{quote}

@@

The above examples all share the same social network structure of small groups connected through mutual membership: {\em interlocks}.
Interlocks have been well-studied in several other contexts.
Perhaps the most well-known is the study of intelocking directorates,
the practice of one individual sitting on the board of directors for
multiple corporations,
allowing an implicit flow of information and influence
\cite{sapinski_interlocking_2018}.
Interlocks arise in other fields as well,
including revolutionary cells
\cite{fishcer_paul_1994, healey_using_2013},
the UK suffragette movement \cite{crossley_covert_2012},
and the global network of cities \cite{taylor_world_2015}.

\subsection{Participatory Governance and Social Learning}
This paper touches on several related topics, namely: problem-solving, decision-making, deliberation, and social learning.
These concepts are very closely related, but not equivalent,
potentially leading to confusion.
Matters are made worse by differing (and conflicting) definitions in the literature.
Here, we attempt to untangle this conceptual knot.

The motivation and ultimate focus of our work is {\em participatory governance}
in the sense Elinor Ostrom's third design principle for long-suriving resource regimes: that ``most of the individuals affected by a resource
regime can participate in making and modifying their rules.''
\cite{ostrom_collective_2000}
In this sense, governance is largely about {\em decision-making} regarding
rules and their enforcement.
But we are careful to note that rules and decisions can take many forms,
both formal and informal.

\subsubsection{Deliberation}
{\em Deliberation} is an exemplar of participatory governance.
But prior to the internet and other forms of digital communication,
the logistics of large-scale governance generally excluded more participatory
forms of decision-making \cite{ackerman_deliberation_2002}.
More tractable alternatives such as voting and representative
assemblies are less participatory.
There is no consensus on the exact definition of deliberation.
We will follow the ``minimalist'' definition proposed by Dryzek
\cite{dryzek_deliberative_2002} and refined by Mansbridge \cite{mansbridge_minimalist_2015}:
\begin{quote}
Deliberation is mutual communication that involves weighing and reflecting on preferences, values and interests regarding matters of common concern.
\end{quote}
Note that this definition does not actually require the making of a decision, but by explicitly mentioning ``preferences," does imply the existence of a decision to be considered.
And again, while ``deliberation'' may conjure images of formal institutions,
note that the above definition includes both formal and informal communication,
as long as it is mutual and non-coercive.

\subsubsection{Social Learning}
In {\em social learning}, individuals revise their beliefs by observing and interacting with others.
Social learning allows an individual to augment their limited information and perspective by observing others who may have different information
and perspectives.
When this observation takes the form of mutual communication,
social learning fits the above definition of deliberation quite well.
In fact, many models of social learning do assume mutual communication
\cite{golub_naive_2010, lazer_network_2007, mason_collaborative_2012, barkoczi_social_2016, gomez_clustering_2019}
and can just as easily be seen as models of deliberation.
Deliberation is a special case of social learning.

Social learning and problem solving

putting it all together
